### 2015-04-29 writing/F'14 paper/quantifiers.tex
Lattice edge tokens; better configs; optimizations

In each run, we sample 20\% of the 60k generated pairs to test on and 
train on the remainder. In this setting, each model must learn a
complete reasoning system for the limited language and logic presented
in the training data, and must be able
to recognize all of the lexical relations between the nouns, verbs,
and quantifiers and how they interact. For instance, it might see
pairs like \eqref{p1} and \eqref{p2} in training and be required to 
then label \eqref{p3}.

>>>>

In each run, we partition the full set of possible sentences under the grammar into training and test sentences, and label all of the pairs from within each set to generate a training set of 27k pairs and a test set of 7k pairs. Because the model doesn't see the test sentences at training time, it cannot directly use the kind of reasoning described in \S\ref{sec:join}, each model must learn a
complete reasoning system for the limited language and logic presented
in the training data, and must be able
to recognize all of the lexical relations between the nouns, verbs,
and quantifiers and how they interact. For instance, it might see
pairs like \eqref{p1} and \eqref{p2} in training and be required to 
then label \eqref{p3}.
